---
header-includes:
  \usepackage[breaklinks]{hyperref}
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
mainfont: Georgia
sansfont: Arial
fontsize: 16pt
urlcolor: blue
title: "Harris Student Government Finance Committee Transparency Report"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F, message = F)
quarter <- params$quarter
```

# Harris Student Government Finance Committee Transparency Report `r quarter`

```{r data}
source("report.R")
df <- setup(quarter)
```

## Summary
The overall budget for `r quarter` was `r dollar_format()(sum(summarize(group_by(df,org),n=mean(totalreceived))["n"],na.rm=T))`.

In `r quarter`, HSG Finance Committee funded `r nrow(summarize(group_by(df,org),n=n()))` HSOs, which reported `r sum(summarize(group_by(df,org),n=mean(attendactual,na.rm=T))["n"],na.rm=T)` attendees across `r sum(summarize(group_by(df,org),n=mean(eventsactual))["n"],na.rm=T)` events in their post-quarter reviews. 

Breakdowns by event type, item type, and organization are included in this transparency report. 

Funding criteria used in this round included:

* Collaboration with other HSOs or non-Harris organizations
* Speaker events and career events (prioritize events that are open to the broader Harris community), see page 5
* Diversity and inclusion (inviting speakers of color, speakers who are disabled or are women)
* How much non-HSG funding each HSO has access to (including rollover from previous quarters, non-Harris grants, or non-Harris RSO funding), see page 3
* Detailed, itemized documentation with regards to planned expenses and justification for why unusual expenses are necessary

Planned improvements for next quarter are included at the end of this document.

\newpage 

## Allocations by Organization

The minimum amount received by any HSO was \$`r min(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)` and the maximum was \$`r max(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)`.

```{r, fig.height = 6.5}
allocations_by_org(quarter, caption = "")
```

\newpage 

## Funding Criteria: Existing and External Funds 

Organizations with large amounts of unexplained rollover received limited funding.

```{r, fig.height = 5}
compare_rollover_allocation(quarter)
```

\newpage 

## Funding Outcomes: Planned versus Actual Spending

```{r, fig.height = 7}
planned_spending(quarter, caption = "Note: Gold=Planned, Maroon=Actual.")
```

\newpage 

## Funding Outcomes: Number of Events

```{r, fig.height = 7}
planned_events(quarter, caption = "Note: Gold=Planned, Maroon=Actual.")
```

\newpage 

```{r,include=F}
compare_allocation_events(caption = "Low allocation not associated with number of canceled events")
```

## Spending by Event Type

We allocated funds on an organizational level, not on an item-by-item basis. While we collected total actual spending for fall quarter per HSO, the following analyses are estimates based on the proportion of funding requests dedicated to each category. For example, if 38\% of requests by Asian Policy Forum related to their annual Southeast Asian cultural show. We would scale this proportion by the total amount awarded to estimate the amount that would have been spent on cultural events. In this analysis, we only considered funds allocated by HSG, not external grants or funds.

Notation:

* **Social**: e.g., retreats, happy hours, mixers, study hours, and alumni events
* **Speaker**: e.g., presentations, lunch \& learns, and panels, usually about policy topics
* **Community engagement**: e.g., volunteering and off-campus events
* **Promotion**: e.g., graphic design, and recruitment activities
* **Workshop**: e.g., career fairs and writing workshops

```{r, fig.height = 3}
spending_by_event_type(quarter)
```

## Spending by Item Type

See previous section for a description of how these items were calculated.

Notation:

* **Services**: e.g.,  bartending, space rental, transportation, event tickets, and food delivery
* **Gifts**: e.g.,  speaker honorariums, promotional merchandise, and raffle prizes
* **Reusable supplies**: e.g., board games and decorations
* **Non-reusable supplies**: e.g., utensils and firewood

```{r, fig.height = 3}
spending_by_item_type(quarter)
```

## Future improvements

Improvement goals for next quarter:

\vspace{30pt}

Sincerely,

FIRST LAST, Finance Committee Chair

FIRST LAST, Second-Year Finance Committee Member

FIRST LAST, Second-Year Finance Committee Member

FIRST LAST, Second-Year Finance Committee Member

FIRST LAST, First-Year Finance Committee Member

FIRST LAST, First-Year Finance Committee Member

FIRST LAST, First-Year Finance Committee Member
