---
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
mainfont: Georgia
sansfont: Arial
fontsize: 16pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F,message = F)
library(tidyverse)
```

# HSG Finance Committee Transparency Report Fall 2024

```{r}
df = read.csv("2024.csv")
hours = read.csv("hours.csv")

df <- df %>%
  group_by(org) %>%
  mutate(
    totalrequested=sum(amount),
    org=str_wrap(org,40)
  )

style <- function(p,dist=200,dollars=T) {
  p <- p  +
    xlab("") +
    ylab("") +
    coord_flip() +
    theme_classic() +
    theme(
      axis.line.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.line.x=element_blank(),
      axis.ticks.x=element_blank(),
      panel.grid.major.x=element_line(color="gray80"),
      plot.margin=unit(c(0,0,0,0), "pt"),
      text = element_text(family = "Georgia")
    )
  
  if (dollars) {
    p <- p +
    scale_y_continuous(
      breaks = seq(0,10000,by=dist),
      labels = scales::dollar_format()
    )
  }

  return(p)
}
```

## Summary

In Fall 2024, HSG Finance Committee met `r nrow(hours)` times for a total of `r sum(hours$minutes)` minutes.

There were two rounds of allocations:

* Main allocations: \$16,090
* Special allocations: \$2,500

HSG funded `r sum(summarize(group_by(df,org),n=mean(nevents
))["n"])` events across `r nrow(summarize(group_by(df,org),n=n()))` HSOs. HSOs requested a total of \$`r floor(sum(df$amount,na.rm=T)/1000)`,000; the overall budget for Fall 2024 was \$18,590.

Special allocations were released due to the HSG Executive Board decision to replace the annual spring Harris Gala with a less costly celebration. Historically, the Harris Gala cost over \$30,000 annually. 

## Allocations by Organization

The minimum amount received by any HSO was \$`r min(summarize(group_by(df,org),amount)["amount"],na.rm=T)` and the maximum was \$`r max(summarize(group_by(df,org),amount)["amount"],na.rm=T)`.

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(totalreceived)) %>%
  ggplot(aes(org,total)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(
    title="Allocations by Organization, Fall 2024",
    subtitle="Dotted line represents mean amount allocated"
  ) +
  geom_hline(
    yintercept=mean(df$totalreceived),
    linetype="dotted",
    size=.8
  )

style(p)
```

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(nevents)) %>%
  ggplot(aes(org,total)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="Number of Events Held by Organization, Fall 2024")

style(p,dollars=F) +
  scale_y_continuous(breaks=seq(0,20,2))
```

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(rollover=mean(totalrollover)) %>%
  ggplot(aes(org,rollover)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="Total Rollover/External Funds by Organization, Fall 2024")
  
style(p,2000)
```

## Allocations by Event Type

We allocated funds on an organizational level, not on an item-by-item basis. The following analyses are estimates based on the proportion of funding requests dedicated to each category. For example, 38\% of requests by Asian Policy Forum related to their annual Southeast Asian cultural show. We scaled this proportion by the final amount awarded to Asian Policy Forum, \$1,420. I also assumed that each organization would use at least 20% of their rollover (existing) funds this quarter.

Notation:

* **Community engagement**: e.g., volunteering and off-campus events
* **Promotion**: e.g., graphic design and recruitment activities.

```{r}
p <- df %>%
  group_by(org,category) %>%
  summarize(
    # scale the amount requested by total received + 20% of total rollover
    adjusted=sum(amount)/mean(totalrequested)*(max(totalreceived)+.2*max(totalrollover))
  ) %>%
  group_by(category) %>%
  summarize(adjusted=round(sum(adjusted))) %>%
  filter(!is.na(adjusted)) %>%
  mutate(
    category=fct_reorder(str_to_sentence(category), adjusted)
  ) %>%
  ggplot(aes(category,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="Allocations by Event Type, Fall 2024",
       subtitle="Estimated from amount requested per category")

style(p,dist=1000)
```

## Allocations by Item Type

Notation:

* **Services**: e.g.,  bartending, event rental, transportation, event tickets, and food delivery
* *Gifts**: e.g.,  speaker honorariums, promotional merchandise, and raffle prizes
* **Reusable supplies**: e.g., board games and decorations
* **Non-reusable supplies**: e.g., utensils and firewood

```{r}
p <- df %>%
  group_by(org,type) %>%
  summarize(
    # scale the amount requested by 
    adjusted=sum(amount)/mean(totalrequested)*mean(totalreceived)
  ) %>%
  group_by(type) %>%
  summarize(adjusted=round(sum(adjusted))) %>%
  filter(!is.na(adjusted)) %>%
  mutate(
    type=fct_reorder(str_to_sentence(type), adjusted)
  ) %>%
  ggplot(aes(type,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="Allocations by Item Type, Fall 2024",
       subtitle="Estimated from amount requested per item type")

style(p,dist=1000)
```

## Survey

**We need your voice** to determine what types of events we, as the Harris student body, want to fund next quarter. Please fill the following 1-minute form to let us know your opinion.

## Future improvements

Improvements for next quarter: (use slides)

* **Expedite funding timelines**
  * HSOs reported unusually slow funding timelines, due to institutional knowledge loss from last year's government. Next quarter, HSOs can expect to receive funding by Week 1.
* **Increase funding transparency**
  * HSOs reported being unclear on what criteria were being used to fund activities. For the Winter 2025 cycle, we released a new [budgeting template]() and new [funding criteria]() to address these issues.
  
Sincerely,

Tony Jiang, Finance Committee Chair

Karen Yi, Finance Committee Member

Andrea , Finance Committee Member

Shivani Patel, Finance Committee Member

Faris, Finance Committee Member

Moe, Finance Committee Member

Tiffany Tu, Finance Committee Member
