---
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
mainfont: Georgia
sansfont: Arial
fontsize: 16pt
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F,message = F)
library(tidyverse)
```

# HSG Finance Committee Transparency Report Fall 2024

```{r}
df = read.csv("2024.csv")
hours = read.csv("hours.csv")

df <- df %>%
  group_by(org) %>%
  mutate(
    totalrequested=sum(amount),
    org=str_wrap(org,60)
  ) %>%
  ungroup() %>%
  mutate(
    org=factor(org,levels=rev(unique(org)),ordered=T)
  )

style <- function(p,dist=200,dollars=T) {
  p <- p  +
    xlab("") +
    ylab("") +
    coord_flip() +
    theme_classic(base_family = "serif") +
    theme(
      axis.line.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.line.x=element_blank(),
      axis.ticks.x=element_blank(),
      panel.grid.major.x=element_line(color="gray80"),
      plot.margin=unit(c(10,10,10,10), "pt")
    )
  
  if (dollars) {
    p <- p +
    scale_y_continuous(
      breaks = seq(0,10000,by=dist),
      labels = scales::dollar_format()
    )
  }

  return(p)
}
```

## Summary

In Fall 2024, HSG Finance Committee met `r nrow(hours)` times for a total of `r sum(hours$minutes)` minutes.

There were two rounds of allocations:

* Main allocations: \$16,090
* Special allocations*: \$2,500

HSG funded `r sum(summarize(group_by(df,org),n=mean(nevents
))["n"])` planned events across `r nrow(summarize(group_by(df,org),n=n()))` HSOs. HSOs requested a total of \$`r floor(sum(df$amount,na.rm=T)/1000)`,000; the overall budget for Fall 2024 was \$18,590.

\* *The HSG Executive Board voted to replace the annual spring Harris Gala with a less costly celebration. Historically, the Harris Gala cost over \$30,000. This release of funds allowed the Finance Committee to hold special allocations in mid-quarter.* 

## Allocations by Organization

The minimum amount received by any HSO was \$`r min(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)` and the maximum was \$`r max(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)`.

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(totalreceived)) %>%
  ggplot(aes(org,total)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(
    title="    Allocations by Organization, Fall 2024",
    subtitle="     Dotted line represents average allocation"
  ) +
  geom_hline(
    yintercept=mean(summarize(group_by(df,org),m=mean(totalreceived,na.rm=T))[["m"]],na.rm=T),
    linetype="dotted",
    size=.6
  )

style(p)
```

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(nevents)) %>%
  ggplot(aes(org,total)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="    Number of Events Planned\n    by Organization, Fall 2024")

style(p,dollars=F) +
  scale_y_continuous(breaks=seq(0,20,2))
```

```{r, fig.height = 6}
p <- df %>%
  group_by(org) %>%
  summarize(rollover=mean(totalrollover)) %>%
  ggplot(aes(org,rollover)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="    Total Rollover/External Funds by\n    Organization, Fall 2024")
  
style(p,2000)
```

## Allocations by Event Type

We allocated funds on an organizational level, not on an item-by-item basis. The following analyses are estimates based on the proportion of funding requests dedicated to each category. For example, 38\% of requests by Asian Policy Forum related to their annual Southeast Asian cultural show. We scaled this proportion by the final amount awarded to Asian Policy Forum, \$1,420. I also assumed that each organization would use at least 20% of their rollover (existing) funds this quarter.

Notation:

* **Social**: e.g., retreats, happy hours, mixers, study hours, and alumni events
* **Speaker**: e.g., presentations, lunch & learns, and panels, usually about policy topics
* **Community engagement**: e.g., volunteering and off-campus events
* **Promotion**: e.g., graphic design, and recruitment activities
* **Workshop**: e.g., career fairs and writing workshops

```{r, fig.height = 3}
p <- df %>%
  group_by(org,category) %>%
  summarize(
    # scale the amount requested by total received + 20% of total rollover
    adjusted=sum(amount,na.rm=T)/mean(totalrequested,na.rm=T)*(max(totalreceived,na.rm=T)+.2*max(totalrollover,na.rm=T))
  ) %>%
  group_by(category) %>%
  summarize(adjusted=round(sum(adjusted,na.rm=T))) %>%
  filter(!is.na(adjusted),category!="") %>%
  mutate(
    category=fct_reorder(str_to_sentence(category), adjusted)
  ) %>%
  ggplot(aes(category,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="   Allocations by Event Type, Fall 2024",
       subtitle="    Estimated from amount requested per category")

style(p,dist=1000)
```

## Allocations by Item Type

See previous section for a description of how these items were calculated.

Notation:

* **Services**: e.g.,  bartending, space rental, transportation, event tickets, and food delivery
* **Gifts**: e.g.,  speaker honorariums, promotional merchandise, and raffle prizes
* **Reusable supplies**: e.g., board games and decorations
* **Non-reusable supplies**: e.g., utensils and firewood

```{r, fig.height = 3}
p <- df %>%
  group_by(org,type) %>%
  summarize(
    # scale the amount requested by 
    adjusted=sum(amount,na.rm=T)/mean(totalrequested,na.rm=T)*mean(totalreceived,na.rm=T)
  ) %>%
  group_by(type) %>%
  summarize(adjusted=round(sum(adjusted,na.rm=T))) %>%
  filter(!is.na(adjusted),type!="") %>%
  mutate(
    type=fct_reorder(str_to_sentence(type), adjusted)
  ) %>%
  ggplot(aes(type,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="   Allocations by Item Type, Fall 2024",
       subtitle="    Estimated from amount requested per item type")

style(p,dist=1000)
```

## Survey

**We need your voice** to determine what types of events we, as the Harris student body, want to fund next quarter. Please fill the following <span style="text-decoration:underline">[1-minute form](https://forms.gle/Jq5z4rwTVAKWb9re8)</span> to let us know your opinion.

## Future improvements

Improvements for next quarter:

* **Expedite funding timelines**
  * HSOs reported unusually slow funding timelines, due to institutional knowledge loss from last year's government. Next quarter, HSOs can expect to receive funding by Week 1.
* **Increase funding transparency**
  * HSOs reported being unclear on what criteria were being used to fund activities. For the Winter 2025 cycle, we released a new <span style="text-decoration:underline">[budgeting template](https://docs.google.com/spreadsheets/d/1frBcdAxVfhK3QXdHX1ozkQUmYlt2pTsr/edit?rtpof=true&gid=1695333964#gid=1695333964)</span> and new <span style="text-decoration:underline">[funding criteria](https://docs.google.com/spreadsheets/d/1uyt3Tjdp7T0ieYMFBzvp8Yh_i8PVPX5L/edit?gid=1230391486#gid=1230391486)</span> to address these issues.

\vspace{12pt}

Sincerely,

Tony Jiang, Finance Committee Chair

Karen Yi, Finance Committee Member

Andrea Kimpson, Finance Committee Member

Shivani Patel, Finance Committee Member

Faris Alrakhis, Finance Committee Member

Moe Alsharif, Finance Committee Member

Tiffany Tu, Finance Committee Member
