---
header-includes:
  \usepackage[breaklinks]{hyperref}
output:
  pdf_document: 
    latex_engine: xelatex
  html_document: default
mainfont: Georgia
sansfont: Arial
fontsize: 16pt
urlcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F,message = F)
library(tidyverse)
```

# Harris Student Government Finance Committee Transparency Report Fall 2024

```{r}
df = read.csv("2024.csv")
hours = read.csv("hours.csv")

df <- df %>%
  group_by(org) %>%
  mutate(
    totalrequested=sum(amount),
    org=str_wrap(org,60)
  ) %>%
  ungroup() %>%
  mutate(
    org=factor(org,levels=rev(unique(org)),ordered=T)
  )

barstyle <- function(p,dist=200,dollars=T) {
  p <- p  +
    xlab("") +
    ylab("") +
    coord_flip() +
    theme_classic(base_family = "serif") +
    theme(
      axis.line.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.line.x=element_blank(),
      axis.ticks.x=element_blank(),
      panel.grid.major.x=element_line(color="gray80"),
      plot.margin=unit(c(10,10,10,10), "pt")
    )
  
  if (dollars) {
    p <- p +
    scale_y_continuous(
      breaks = seq(0,50000,by=dist),
      labels = scales::dollar_format()
    )
  }

  return(p)
}


pointstyle <- function(p,dist=200,dollars=T) {
  p <- p  +
    theme_classic(base_family = "serif") +
    theme(
      axis.line.y=element_blank(),
      axis.ticks.y=element_blank(),
      axis.line.x=element_blank(),
      axis.ticks.x=element_blank(),
      panel.grid.major.x=element_line(color="gray80"),
      panel.grid.major.y=element_line(color="gray80"),
      plot.margin=unit(c(10,10,10,10), "pt"),
      aspect.ratio=1
    )
  
  if (dollars) {
    p <- p +
    scale_x_continuous(
      breaks = seq(0,50000,by=dist),
      labels = scales::dollar_format()
    ) +
    scale_y_continuous(
      breaks = seq(0,50000,by=200),
      labels = scales::dollar_format()
    )
  }

  return(p)
}
```

## Summary

The overall budget for Fall 2024 was \$18,590, which were allocated in two rounds:

* Main allocations: \$16,090
* Special allocations*: \$2,500

In Fall 2024, HSG Finance Committee met `r nrow(hours)` times for a total of `r sum(hours$minutes)` minutes. HSG funded `r nrow(summarize(group_by(df,org),n=n()))` HSOs, which reported `r sum(summarize(group_by(df,org),n=mean(attendactual))["n"],na.rm=T)` attendees across `r sum(summarize(group_by(df,org),n=mean(eventsactual))["n"],na.rm=T)` events in their post-fall quarter reviews. 

Breakdowns by event type, item type, and organization are included in this transparency report. Please use the survey at the end of this report to send us comments, suggestions, or questions about this report or HSG Finance Committee activities in general.

Funding criteria used in this round included:

* Collaboration with other HSOs or non-Harris organizations
* Speaker events and career events (prioritize events that are open to the broader Harris community), see page 5
* Diversity and inclusion (inviting speakers of color, speakers who are disabled or are women)
* How much non-HSG funding each HSO has access to (including rollover from previous quarters, non-Harris grants, or non-Harris RSO funding), see page 3
* Detailed, itemized documentation with regards to planned expenses and justification for why unusual expenses are necessary

As we note in a later section, additional criteria and more quantified criteria have been added for winter quarter.

^[*The HSG Executive Board voted to replace the annual spring Harris Gala with a less costly celebration. Historically, the Harris Gala cost over \$30,000. This release of funds allowed the Finance Committee to hold special allocations in mid-quarter.] 

\newpage 

## Allocations by Organization

The minimum amount received by any HSO was \$`r min(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)` and the maximum was \$`r max(summarize(group_by(df,org),totalreceived)["totalreceived"],na.rm=T)`.

```{r, fig.height = 6.5}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(totalreceived)) %>%
  ggplot(aes(org,total)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(
    title="   Allocations by Organization, Fall 2024",
    subtitle="   Dotted line represents average allocation",
    caption="Note: BePP did not submit a budget request"
  ) +
  geom_hline(
    yintercept=mean(summarize(group_by(df,org),m=mean(totalreceived,na.rm=T))[["m"]],na.rm=T),
    linetype="dotted",
    size=.6
  )

barstyle(p)
```


```{r, fig.height = 6, include=F}
p <- df %>%
  group_by(org) %>%
  summarize(leftover=mean(totalreceived,na.rm=T) + mean(externalreceived,na.rm=T) + mean(totalrollover,na.rm=T) - mean(actual,na.rm=T)) %>%
  ggplot(aes(org,leftover)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(
    title="   New Rollover by Organization, Fall 2024",
    subtitle="   Dotted line represents average allocation",
    caption=""
  ) +
  geom_hline(
    yintercept=mean(summarize(group_by(df,org),m=mean(totalreceived,na.rm=T))[["m"]],na.rm=T),
    linetype="dotted",
    size=.6
  )

barstyle(p,dist=1000)
```

\newpage 

## Funding Criteria: Existing and External Funds 

Organizations with large amounts of unexplained rollover received limited funding.

```{r, fig.height = 5}
rollover <- df %>%
  group_by(org) %>%
  summarize(rollover=mean(totalrollover+externalreceived),
            received=mean(totalreceived))

p <- rollover %>%
  ggplot(aes(rollover,received)) +
  geom_point(color="#800000") +
  labs(
    title="   Allocations Compared to Rollover +\n   External Funding by Organization, Fall 2024"
    # subtitle="   Points represent rollover/external amount"
  ) +
  xlab("Rollover + external funding") +
  ylab("Received") 
  # geom_smooth(method="lm")

# not significant
# lm(received~rollover, rollover) %>% summary()

pointstyle(p,dist=2000)
```
\newpage 

## Funding Outcomes: Number of Events

The trend revealed here is to expect HSOs to generally held less events than planned, likely due to a limited amount of funding overall (scarce resources). 

The general distribution of events remains the same when comparing planned versus held events: the HSOs who planned the most events held the most events, and those who planned the least events held the least events.

```{r, fig.height = 7}
p <- df %>%
  group_by(org) %>%
  summarize(total=mean(eventsactual),
            planned=mean(events.planned)) %>%
  filter(!is.na(total)) %>%
  ggplot() +
  geom_bar(
    aes(org,planned,fill=Category),
    stat="identity",
    fill="#C16622"
  ) +
  geom_bar(
    aes(org,total,fill=Category),
    stat="identity",
    fill="#800000"
  ) +
  labs(
    title="   Planned vs. Actual Number of Events Held\n   by Organization, Fall 2024",
    caption="   Note: Gold=Planned, Maroon=Actual. IDPA and TAP did not report how many events they held in Fall"
  )

barstyle(p,dollars=F) +
  scale_y_continuous(breaks=seq(0,20,2))
```

\newpage 

```{r,include=F}
# is receiving a low amount of funding correlated with hosting less events than planned?
df$devents <- df$events.planned-df$eventsactual
lm(totalreceived~devents,df) %>% summary()

p <- df %>%
  ggplot(aes(totalreceived,devents)) +
  geom_point(color="#800000") +
  xlab("Allocation") +
  ylab("Number of events canceled") +
  labs(title="Low allocation not associated with number of canceled events")

pointstyle(p,dollars=F)
```

## Spending by Event Type

```{r}
# if we don't know how much they spent, assume received plus some rollover
df[is.na(df$actual),"actual"] <- df[is.na(df$actual),"totalreceived"] + df[is.na(df$actual),"externalreceived"] + round(df[is.na(df$actual),"totalrollover"] * .2)
```


We allocated funds on an organizational level, not on an item-by-item basis. While we collected total actual spending for fall quarter per HSO, the following analyses are estimates based on the proportion of funding requests dedicated to each category. For example, 38\% of requests by Asian Policy Forum related to their annual Southeast Asian cultural show. We scaled this proportion by the total amount awarded, \$1,420, to estimate the amount that would have been spent on cultural events. In this analysis, we only considered funds allocated by HSG, not external grants or funds.

Notation:

* **Social**: e.g., retreats, happy hours, mixers, study hours, and alumni events
* **Speaker**: e.g., presentations, lunch \& learns, and panels, usually about policy topics
* **Community engagement**: e.g., volunteering and off-campus events
* **Promotion**: e.g., graphic design, and recruitment activities
* **Workshop**: e.g., career fairs and writing workshops

```{r}
# recalculate total requested for only those events held
df <- df %>%
  filter(actual!=0) %>%
  group_by(org) %>%
  mutate(totalrequested=sum(amount,na.rm=T))

# cap actual spent by amount we granted
df <- mutate(df,actualhsg=min(totalreceived,actual))
```

```{r, fig.height = 3}
p <- df %>%
  group_by(org,category) %>%
  summarize(
    # we are missing detailed information for actual spending, so impute:
    # scale the amount requested by actual spending
    adjusted=sum(amount,na.rm=T)/mean(totalrequested,na.rm=T)*mean(actualhsg,na.rm=T)
  ) %>%
  group_by(category) %>%
  summarize(adjusted=round(sum(adjusted,na.rm=T))) %>%
  filter(!is.na(adjusted),category!="") %>%
  mutate(
    category=fct_reorder(str_to_sentence(category), adjusted)
  ) %>%
  ggplot(aes(category,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="    HSG Funds Spending by Event Type, Fall 2024",
       subtitle="     Estimated from amount requested per category")

barstyle(p,dist=1000)
```

## Spending by Item Type

See previous section for a description of how these items were calculated.

Notation:

* **Services**: e.g.,  bartending, space rental, transportation, event tickets, and food delivery
* **Gifts**: e.g.,  speaker honorariums, promotional merchandise, and raffle prizes
* **Reusable supplies**: e.g., board games and decorations
* **Non-reusable supplies**: e.g., utensils and firewood

```{r, fig.height = 3}
p <- df %>%
  group_by(org,type) %>%
  summarize(
    # scale the amount requested by 
    adjusted=sum(amount,na.rm=T)/mean(totalrequested,na.rm=T)*mean(actualhsg,na.rm=T)
  ) %>%
  group_by(type) %>%
  summarize(adjusted=round(sum(adjusted,na.rm=T))) %>%
  filter(!is.na(adjusted),type!="") %>%
  mutate(
    type=fct_reorder(str_to_sentence(type), adjusted)
  ) %>%
  ggplot(aes(type,adjusted)) +
  geom_bar(stat="identity",show.legend=F,fill="#800000") +
  labs(title="    HSG Funds Spending by Item Type, Fall 2024",
       subtitle="     Estimated from amount requested per item type")

barstyle(p,dist=2000)
```

```{r,include=F}
uniques <- distinct(df,actual,externalreceived,totalreceived,totalrollover,eventsactual,events.planned,attendactual,totalrequested)

lm(totalreceived~events.planned+totalrollover+externalreceived,uniques) %>% summary()
```


## Future improvements

Improvement goals for winter quarter:

* **Expedite funding timelines**
  * HSOs reported unusually slow funding timelines, due to institutional knowledge loss from last year's government. This quarter, HSGs finished funding decisions by week 1. Unfortunately, due to turnover within the Student Engagement staff teams, we were not able to allocate funds within week 1 as originally planned.
* **Increase funding transparency**
  * HSOs reported being unclear on what criteria were being used to fund activities. For the Winter 2025 cycle, we released a new \href{https://tinyurl.com/4yx98367}{\underline{budgeting template}} and new \href{https://docs.google.com/spreadsheets/d/1hAO4El9QERUdx8u9yyNmK4RZuDeH7MHo/edit?usp=sharing&ouid=105056093794884384969&rtpof=true&sd=true}{\underline{funding criteria}} to address these issues. Funding committee members now use a rubric-standardized process to evaluate funding items. Standard deviation on winter allocations decreased by $127 compared to fall allocations. 

## Survey

**We need your voice** to determine what types of events we, as the Harris student body, want to fund next quarter. Please fill the following \href{https://forms.gle/Jq5z4rwTVAKWb9re8}{\underline{1-minute form}} to let us know your opinion.

\vspace{30pt}

Sincerely,

Tony Jiang, Finance Committee Chair

Karen Yi, Second-Year Finance Committee Member

Andrea Kimpson, Second-Year Finance Committee Member

Shivani Patel, Second-Year Finance Committee Member

Faris Alrakhis, First-Year Finance Committee Member

Moe Alsharif, First-Year Finance Committee Member

Tiffany Tu, First-Year Finance Committee Member
